How do school travel planning stakeholders frame active school travel in Ontario, Canada?

### 2021-08-06 AST-Framing-Ontario/AST-Framing-Ontario.tex
KWIC completed and TM in progress

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={How do school travel planning stakeholders frame active school travel in Ontario, Canada?},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

To increase rates of walking and bicycling independently to school,
Riazi et al.~({\textbf{???}}) state: ``it will be vital for
interventions to target modifiable factors, including children's and
parents' perceptions of their social environment.'' Parents play the
important role of ``gatekeeper'' by either granting or restricting CIM
licenses, meaning whether children can travel alone ({\textbf{???}}).
For this reason, stakeholders involved in STP produce information
targeted for both children and parents, and aim to involve the broader
community in their efforts to increase the number of children walking
and bicycling to school..

@@

Any goals for AST, and also CIM, ought to be clearly articulated and
reflected in transportation plans and policies to guide initiatives.
Presently, however, there has been no study to date that explores how
Canadian municipalities and schools frame and discuss AST with the
public. Content analysis is one method to analyze how particular issues
are framed to groups of people, for instance parents or educators who
might be inclined to support AST. It attempts to understand how
information presented from a ``communicator'' leads the ``receiver'' to
a desired response ({\textbf{???}}). In a recent paper ({\textbf{???}}),
framing analysis was applied to review municipal policies addressing
climate change in four western Canadian cities. Natural language
processing (NLP) was used for a similar purpose to examine content in
general plans from Californian cities ({\textbf{???}}). The way policy
issues are framed is important to understand because it plays a role in
either altering or preserving the existing social perceptions.

@@

The aim of this paper is to analyze how AST is framed by STP
stakeholders in Ontario, Canada. We used topic modelling and qualitative
content analysis to examine how the benefits and barriers of AST are
presented to the public and which solutions for improving AST are
identified in local policy documents from Ontario municipalities and
school boards. We compared these documents to a selection of studies on
AST to explore the extent to which research findings have trickled down
to inform policy and planning for AST interventions.

@@

We then assembled a collection of publicly available documents that were
sourced online from the main stakeholder groups involved in STP
initiatives in Ontario: i) English school boards; ii) municipal
government; and iii) transportation consortia. Non-profit organizations,
police services, and advocacy groups are other stakeholders who may play
a role in supporting AST and/or STP, but this study does not include any
documents from these groups because they are not consistently
participating in initiatives.

The search was guided first by a list of all English school boards
across Ontario. The websites of each school board were searched for
pages related to transportation or school travel. These pages were
manually downloaded. Next, we collected documents by searching municipal
government and transportation consortia websites. The latter were
identified based on geographic area (i.e., the municipalities and/or
transportation consortia who are in the same geographic area of each
school board). Pages related to active transportation or school travel
were manually downloaded. Webpages were included in the corpus if they
were easy to find. This primary criteria was important since our
analysis pertains to how such issues are framed to the public. Thus,
these pages ought to be easy to find, which we defined as requiring no
more than 2-4 separate links from the initial Google search.

The initial corpus of policy documents included 64 relevant webpages
(i.e., one page or more) from all main stakeholder groups. It is
important to note that school boards, municipalities, and transportation
consortia may or may not publish information about their involvement in
AST and STP efforts on their respective websites or in policy documents.
Search results are summarized in Table \ref{tab:policy-documents}.

@@

\caption{\label{tab:policy-documents}\label{tab:search-results}Search results from the main STP stakeholder groups.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{>{}l|>{\raggedright\arraybackslash}p{30em}|>{}l}
\toprule
Stakeholder & Total & Included\\
\midrule
\cellcolor{gray!6}{\textbf{English school boards}} & \cellcolor{gray!6}{62} & \cellcolor{gray!6}{31}\\
\textbf{Municipalities or regions} & 62 & 25\\
\cellcolor{gray!6}{\textbf{Transportation consortia}} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{8}\\
\bottomrule
\end{tabular}}
\end{table}

@@

Next, we converted the trimmed PDF documents into \texttt{txt} files so
that they could be imported in \texttt{R} for topic modelling. We then
proceeded to a manual cleaning phase where we removed any remaining
tables, figures, references, headers/footings, and captions that could
not be trimmed. Manual corrections were also required for certain pages
in academic papers that remained in two-column format after the
conversion process. This typically occurred on pages that had a table or
figure which disrupted the text. Finally, we reviewed all of the
documents to remove hyphenation by line breaks and to keep hyphenated
words together on the same line. Any ligatures (e.g., combinations of
characters or letters that were not properly detected during the
conversion process) were fixed by inserting the unicode sequence of
character to replace the missing sequence of characters.

@@

In the final step before analysis, we removed all blank spaces,
punctuation, capitalization, and numbers. English stop words, which are
common words such as \emph{and} or \emph{the} as identified in a
predetermined list by Lewis et al.~({\textbf{???}}) and other frequent
terms in the documents like ``school'' and location names were removed
from the corpora.

@@

Natural language processing

Silge and Robinson ({\textbf{???}}) is

We've been using the unnest\_tokens function to tokenize by word, or
sometimes by sentence, which is useful for the kinds of sentiment and
frequency analyses we've been doing so far. But we can also use the
function to tokenize into consecutive sequences of words, called
n-grams. By seeing how often word X is followed by word Y, we can then
build a model of the relationships between them.

We do this by adding the token = ``ngrams'' option to unnest\_tokens(),
and setting n to the number of words we wish to capture in each n-gram.
When we set n to 2, we are examining pairs of two consecutive words,
often called ``bigrams'':

\hypertarget{content-analysis}{%
\subsection{3.2. Content analysis}\label{content-analysis}}

Content analysis is a method to examine content from texts including the
message itself, the sender(s) of the message, the recipients of the
message, or the impact of the message ({\textbf{???}}). Words or phrases
are the unit of analysis. \emph{Qualitative} content analysis

\hypertarget{reproducibility}{%
\subsection{3.3. Reproducibility}\label{reproducibility}}

@@

We analyzed word and document frequency for each corpus. Table
\ref{tab:word-table} presents the most common terms found in the
municipal, transportation consortia, school board, and academic
documents.

@@

\cellcolor{gray!6}{walking} & \cellcolor{gray!6}{90} & \cellcolor{gray!6}{25} & \cellcolor{gray!6}{students} & \cellcolor{gray!6}{119} & \cellcolor{gray!6}{30} & \cellcolor{gray!6}{walk} & \cellcolor{gray!6}{49} & \cellcolor{gray!6}{8} & \cellcolor{gray!6}{distance} & \cellcolor{gray!6}{3271} & \cellcolor{gray!6}{205}\\
bike & 87 & 15 & travel & 103 & 11 & travel & 41 & 8 & students & 2960 & 173\\
\cellcolor{gray!6}{cycling} & \cellcolor{gray!6}{78} & \cellcolor{gray!6}{22} & \cellcolor{gray!6}{student} & \cellcolor{gray!6}{93} & \cellcolor{gray!6}{25} & \cellcolor{gray!6}{students} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{cycling} & \cellcolor{gray!6}{2753} & \cellcolor{gray!6}{171}\\

@@

safety & 71 & 21 & information & 65 & 21 & safety & 32 & 6 & environment & 2631 & 202\\
\cellcolor{gray!6}{health} & \cellcolor{gray!6}{65} & \cellcolor{gray!6}{21} & \cellcolor{gray!6}{schools} & \cellcolor{gray!6}{61} & \cellcolor{gray!6}{19} & \cellcolor{gray!6}{help} & \cellcolor{gray!6}{29} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{activity} & \cellcolor{gray!6}{2371} & \cellcolor{gray!6}{209}\\
physical & 63 & 18 & board & 61 & 26 & schools & 25 & 9 & traffic & 2353 & 208\\
\cellcolor{gray!6}{traffic} & \cellcolor{gray!6}{59} & \cellcolor{gray!6}{20} & \cellcolor{gray!6}{walking} & \cellcolor{gray!6}{57} & \cellcolor{gray!6}{17} & \cellcolor{gray!6}{children} & \cellcolor{gray!6}{25} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{choice} & \cellcolor{gray!6}{2299} & \cellcolor{gray!6}{169}\\
road & 56 & 13 & walk & 53 & 13 & community & 24 & 7 & physical & 2256 & 215\\

@@

\cellcolor{gray!6}{activity} & \cellcolor{gray!6}{55} & \cellcolor{gray!6}{14} & \cellcolor{gray!6}{district} & \cellcolor{gray!6}{50} & \cellcolor{gray!6}{23} & \cellcolor{gray!6}{bus} & \cellcolor{gray!6}{18} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{trips} & \cellcolor{gray!6}{2194} & \cellcolor{gray!6}{170}\\
schools & 52 & 14 & weather & 40 & 11 & route & 17 & 5 & car & 2148 & 195\\
\cellcolor{gray!6}{children} & \cellcolor{gray!6}{47} & \cellcolor{gray!6}{15} & \cellcolor{gray!6}{safety} & \cellcolor{gray!6}{40} & \cellcolor{gray!6}{19} & \cellcolor{gray!6}{zone} & \cellcolor{gray!6}{16} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{safety} & \cellcolor{gray!6}{2140} & \cellcolor{gray!6}{204}\\
plan & 45 & 16 & safe & 39 & 19 & resources & 16 & 6 & time & 2101 & 218\\
\cellcolor{gray!6}{students} & \cellcolor{gray!6}{44} & \cellcolor{gray!6}{14} & \cellcolor{gray!6}{services} & \cellcolor{gray!6}{37} & \cellcolor{gray!6}{17} & \cellcolor{gray!6}{day} & \cellcolor{gray!6}{16} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{factors} & \cellcolor{gray!6}{2101} & \cellcolor{gray!6}{216}\\

@@

walk & 43 & 18 & planning & 37 & 7 & safe & 15 & 5 & child & 2085 & 187\\
\cellcolor{gray!6}{public} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{15} & \cellcolor{gray!6}{parents} & \cellcolor{gray!6}{32} & \cellcolor{gray!6}{17} & \cellcolor{gray!6}{planning} & \cellcolor{gray!6}{15} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{walk} & \cellcolor{gray!6}{2008} & \cellcolor{gray!6}{200}\\
will & 38 & 15 & sustainable & 31 & 8 & physical & 15 & 7 & public & 1983 & 208\\
\cellcolor{gray!6}{community} & \cellcolor{gray!6}{37} & \cellcolor{gray!6}{19} & \cellcolor{gray!6}{may} & \cellcolor{gray!6}{30} & \cellcolor{gray!6}{13} & \cellcolor{gray!6}{healthy} & \cellcolor{gray!6}{14} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{age} & \cellcolor{gray!6}{1783} & \cellcolor{gray!6}{211}\\
safe & 34 & 16 & children & 30 & 14 & traffic & 13 & 6 & urban & 1768 & 200\\

@@

\cellcolor{gray!6}{benefits} & \cellcolor{gray!6}{32} & \cellcolor{gray!6}{17} & \cellcolor{gray!6}{day} & \cellcolor{gray!6}{29} & \cellcolor{gray!6}{13} & \cellcolor{gray!6}{support} & \cellcolor{gray!6}{13} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{home} & \cellcolor{gray!6}{1715} & \cellcolor{gray!6}{199}\\
play & 31 & 2 & child & 29 & 12 & families & 13 & 5 & social & 1713 & 191\\
\cellcolor{gray!6}{resources} & \cellcolor{gray!6}{30} & \cellcolor{gray!6}{13} & \cellcolor{gray!6}{cancellations} & \cellcolor{gray!6}{29} & \cellcolor{gray!6}{13} & \cellcolor{gray!6}{way} & \cellcolor{gray!6}{12} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{different} & \cellcolor{gray!6}{1713} & \cellcolor{gray!6}{215}\\
healthy & 29 & 16 & routes & 28 & 14 & student & 12 & 5 & mobility & 1659 & 138\\
\cellcolor{gray!6}{routes} & \cellcolor{gray!6}{27} & \cellcolor{gray!6}{13} & \cellcolor{gray!6}{physical} & \cellcolor{gray!6}{28} & \cellcolor{gray!6}{11} & \cellcolor{gray!6}{region} & \cellcolor{gray!6}{12} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{significant} & \cellcolor{gray!6}{1650} & \cellcolor{gray!6}{208}\\

@@

\hypertarget{bigrams-and-correlations}{%
\subsection{4.2. Bigrams and
correlations}\label{bigrams-and-correlations}}

Bigrams for each policy corpora are shown in Figures
\ref{fig:city-bigrams}, \ref{fig:consortia-bigrams}, and
\ref{fig:school-bigrams}. These figures help to make further sense of
the word frequencies reported above, and highlight the main ideas that
are presented to the public in each of the policy corpora.
Municipalities primarily discuss ``physical activity'' (n = 53) and
``public health'' (n = 19) in the context of active travel. In addition,
``travel planning'' (n = 19), ``bike lanes'' (n = 16), and ``safe
routes'' (n = 14) are also identified, conceivably as interventions and
built environment factors that support AST. Key issues related to AST
such as ``traffic safety'' (n = 10), ``air quality'' (n = 9), and
``greenhouse gases'' (n = 9) are conveyed to the public but in fewer
documents. Similar word bigrams are found in school board documents:
``travel planning'' (n = 33), ``safe routes'' (n = 15), ``physical
activity'' (n = 10), and ``public health'' (n = 10) are among the most
common bigrams. Unlike other STP stakeholders, school boards also
consider ``inclement weather'' (n = 24) ``bus cancellations'' (n = 13).
This is likely because many students in Ontario travel by school bus and
this information is presented alongside AST. Finally, transportation
consortia documents highlight ``physical activity'' (n = 10),
``pedestrian safety'' (n = 8), ``crossing guards'' (n = 6), ``travel
planning'' (n = 6), and ``walk zones'' (n = 6). Bicycling is notably
absent from transportation consortia documents.

>>>>

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{graphicx}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={How do school travel planning stakeholders frame active school travel in Ontario, Canada?},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

To increase rates of walking and bicycling independently to school,
Riazi et al.~({\textbf{???}}) state: ``it will be vital for
interventions to target modifiable factors, including children's and
parents' perceptions of their social environment.'' Parents play the
important role of ``gatekeeper'' by either granting or restricting CIM
licenses, meaning whether children can travel alone ({\textbf{???}}).
For this reason, stakeholders involved in STP produce information
targeted for both children and parents, and aim to involve the broader
community in their efforts to increase the number of children walking
and bicycling to school.

@@

Any goals for AST, and also CIM, ought to be clearly articulated and
reflected in transportation plans and policies to guide initiatives.
Presently, however, there has been no study to date that explores how
Canadian municipalities and schools frame and discuss AST with the
public. Content analysis is one method to analyze how particular issues
are framed to groups of people, for instance parents or educators who
might be inclined to support AST. It attempts to understand how
information presented from a ``communicator'' leads the ``receiver'' to
a desired response ({\textbf{???}}). In a recent paper ({\textbf{???}}),
framing analysis was applied to review municipal policies addressing
climate change in four western Canadian cities. Natural language
processing (NLP) has also been used for a similar purpose to examine
content in general plans from Californian cities ({\textbf{???}}). The
way policy issues are framed is ultimately important to understand
because it plays a role in either altering or preserving the existing
social perceptions.

@@

The aim of this paper is to analyze how AST is framed by STP
stakeholders in Ontario, Canada. We used text mining and topic modelling
to examine how local policy documents from Ontario municipalities and
school boards present and communicate the benefits and barriers of AST
and the solutions for improving AST. We compared the findings from these
documents to a selection of studies on AST and explored the extent to
which research findings have trickled down to inform policy and planning
for increasing AST.

@@

We assembled a collection of publicly available documents that were
sourced online from the main stakeholder groups involved in STP
initiatives in Ontario: i) school boards (public and English-speaking
only); ii) municipal governments; and iii) transportation consortia.
Non-profit organizations, police services, and advocacy groups are other
stakeholders who may play a role in supporting AST and/or STP, but this
study does not include any documents from these groups because they are
not consistently participating in initiatives.

The search was guided first by a list of all English public school
boards across Ontario. The websites of each school board were manually
searched for pages related to school transportation or travel. Any pages
relevant to these topics were manually downloaded. Next, we collected
documents by searching municipal government and transportation consortia
websites. The latter were identified based on geographic area (i.e., the
municipalities and/or transportation consortia who are in the same
geographic area of each school board). Pages related to active or school
travel were manually downloaded. Webpages from STP stakeholder websites
were included in our analysis if they were easy to find. This primary
criteria was important since our analysis pertains to how such issues
are framed to the public. Thus, we included only webpages that were easy
to find, which we defined as requiring no more than 2-4 separate links
from the initial Google search.

The initial corpus of policy documents included 64 relevant webpages
(i.e., one page or more) from all STP stakeholder groups. It is
important to note that school boards, municipalities, and transportation
consortia may or may not publish information about their involvement in
AST and STP efforts on their respective websites or in policy documents,
which means that some of these groups for particular regions in Ontario
are not included in our analysis. Search results are summarized in Table
\ref{tab:policy-documents}.

@@

\caption{\label{tab:policy-documents}\label{tab:search-results}Search results from the main STP stakeholder groups.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{>{}l|l|>{}l}
\toprule
Stakeholder & Total & Included\\
\midrule
\cellcolor{gray!6}{\textbf{School boards}} & \cellcolor{gray!6}{62} & \cellcolor{gray!6}{31}\\
\textbf{Municipalities} & 62 & 25\\
\cellcolor{gray!6}{\textbf{Transportation consortia}} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{8}\\
\bottomrule
\end{tabular}}
\end{table}

@@

Next, we converted the trimmed PDF documents into \texttt{txt} files so
that they could be imported in R for analysis. We then proceeded to a
manual cleaning phase where we removed any remaining tables, figures,
references, headers/footings, and captions that could not be trimmed.
Manual corrections were also required for certain pages in academic
papers that remained in two-column format after the conversion process.
This typically occurred on pages that had a table or figure which
disrupted the text. Finally, we reviewed all of the documents to remove
hyphenation by line breaks and to keep hyphenated words together on the
same line. Any ligatures (e.g., combinations of characters or letters
that were not properly detected during the conversion process) were
fixed by inserting the unicode sequence of character to replace the
missing sequence of characters.

@@

In the final step, we removed all blank spaces, punctuation,
capitalization, and numbers. English stop words, which are common words
such as \emph{and} or \emph{the} as identified in a predetermined list
by Lewis et al.~({\textbf{???}}) and other frequent terms in the
documents like ``school'' and specific location names, were removed from
the corpora.

@@

\hypertarget{reproducibility}{%
\subsection{3.2. Reproducibility}\label{reproducibility}}

@@

We analyzed word and document frequency for each corpora. Table
\ref{tab:word-table} shows the most frequent terms found in the
municipal, transportation consortia, school board, and academic
documents. As expected, STP documents and academic papers reference
\emph{active travel}, \emph{walking}, \emph{biking} or \emph{cycling},
and \emph{students} more than other terms. Each corpora also has
\emph{safety} and \emph{traffic} as common words which suggests
congruence on these key factors between the research literature and how
AST is framed to the public. The word \emph{physical} is present in each
corpus which could refer to either \emph{physical activity},
\emph{physical health}, or the \emph{physical environment}. Furthermore,
documents from STP stakeholders discuss \emph{resources},
\emph{information}, and \emph{services} about school travel. In the
section below, the context in which these terms appear is explored
further through their concordance. Unlike the academic papers, STP
stakeholder documents include the words \emph{route} or \emph{routes}.
This could reflect their role in identifying safe routes to school to
share with parents or families, as well as the STP emphasis on making
the physical environment safer for AST. The academic corpora differs
from the policy documents in that \emph{parents} and \emph{distance} are
the second and third most common terms. In addition, \emph{time},
\emph{factors}, \emph{environment}, and \emph{age} are also identified
in academic papers. These words are absent from the list of common words
in policy documents. Table \ref{tab:word-table} indicates that the
research corpora discusses a broader range of determinants of AST than
the policy documents. The number of references for each term in the
academic papers is also significantly higher due to the inclusion of
more documents.

@@

\cellcolor{gray!6}{walking} & \cellcolor{gray!6}{90} & \cellcolor{gray!6}{25} & \cellcolor{gray!6}{travel} & \cellcolor{gray!6}{103} & \cellcolor{gray!6}{11} & \cellcolor{gray!6}{walk} & \cellcolor{gray!6}{49} & \cellcolor{gray!6}{8} & \cellcolor{gray!6}{distance} & \cellcolor{gray!6}{3271} & \cellcolor{gray!6}{205}\\
bike & 87 & 15 & information & 65 & 21 & travel & 41 & 8 & students & 2960 & 173\\
\cellcolor{gray!6}{cycling} & \cellcolor{gray!6}{78} & \cellcolor{gray!6}{22} & \cellcolor{gray!6}{walking} & \cellcolor{gray!6}{57} & \cellcolor{gray!6}{17} & \cellcolor{gray!6}{students} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{cycling} & \cellcolor{gray!6}{2753} & \cellcolor{gray!6}{171}\\

@@

safety & 71 & 21 & walk & 53 & 13 & safety & 32 & 6 & environment & 2631 & 202\\
\cellcolor{gray!6}{health} & \cellcolor{gray!6}{65} & \cellcolor{gray!6}{21} & \cellcolor{gray!6}{weather} & \cellcolor{gray!6}{40} & \cellcolor{gray!6}{11} & \cellcolor{gray!6}{help} & \cellcolor{gray!6}{29} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{activity} & \cellcolor{gray!6}{2371} & \cellcolor{gray!6}{209}\\
physical & 63 & 18 & safety & 40 & 19 & schools & 25 & 9 & traffic & 2353 & 208\\
\cellcolor{gray!6}{traffic} & \cellcolor{gray!6}{59} & \cellcolor{gray!6}{20} & \cellcolor{gray!6}{safe} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{19} & \cellcolor{gray!6}{children} & \cellcolor{gray!6}{25} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{choice} & \cellcolor{gray!6}{2299} & \cellcolor{gray!6}{169}\\
road & 56 & 13 & services & 37 & 17 & community & 24 & 7 & physical & 2256 & 215\\

@@

\cellcolor{gray!6}{activity} & \cellcolor{gray!6}{55} & \cellcolor{gray!6}{14} & \cellcolor{gray!6}{planning} & \cellcolor{gray!6}{37} & \cellcolor{gray!6}{7} & \cellcolor{gray!6}{bus} & \cellcolor{gray!6}{18} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{trips} & \cellcolor{gray!6}{2194} & \cellcolor{gray!6}{170}\\
schools & 52 & 14 & parents & 32 & 17 & route & 17 & 5 & car & 2148 & 195\\
\cellcolor{gray!6}{children} & \cellcolor{gray!6}{47} & \cellcolor{gray!6}{15} & \cellcolor{gray!6}{sustainable} & \cellcolor{gray!6}{31} & \cellcolor{gray!6}{8} & \cellcolor{gray!6}{zone} & \cellcolor{gray!6}{16} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{safety} & \cellcolor{gray!6}{2140} & \cellcolor{gray!6}{204}\\
plan & 45 & 16 & children & 31 & 14 & resources & 16 & 6 & time & 2101 & 218\\
\cellcolor{gray!6}{students} & \cellcolor{gray!6}{44} & \cellcolor{gray!6}{14} & \cellcolor{gray!6}{child} & \cellcolor{gray!6}{31} & \cellcolor{gray!6}{12} & \cellcolor{gray!6}{day} & \cellcolor{gray!6}{16} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{factors} & \cellcolor{gray!6}{2101} & \cellcolor{gray!6}{216}\\

@@

walk & 43 & 18 & day & 29 & 13 & safe & 15 & 5 & child & 2085 & 187\\
\cellcolor{gray!6}{public} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{15} & \cellcolor{gray!6}{routes} & \cellcolor{gray!6}{28} & \cellcolor{gray!6}{14} & \cellcolor{gray!6}{planning} & \cellcolor{gray!6}{15} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{walk} & \cellcolor{gray!6}{2008} & \cellcolor{gray!6}{200}\\
community & 37 & 19 & physical & 28 & 11 & physical & 15 & 7 & public & 1983 & 208\\
\cellcolor{gray!6}{safe} & \cellcolor{gray!6}{34} & \cellcolor{gray!6}{16} & \cellcolor{gray!6}{health} & \cellcolor{gray!6}{28} & \cellcolor{gray!6}{11} & \cellcolor{gray!6}{healthy} & \cellcolor{gray!6}{14} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{age} & \cellcolor{gray!6}{1783} & \cellcolor{gray!6}{211}\\
benefits & 32 & 17 & inclement & 25 & 11 & traffic & 13 & 6 & urban & 1768 & 200\\

@@

\cellcolor{gray!6}{play} & \cellcolor{gray!6}{31} & \cellcolor{gray!6}{2} & \cellcolor{gray!6}{eligibility} & \cellcolor{gray!6}{24} & \cellcolor{gray!6}{11} & \cellcolor{gray!6}{support} & \cellcolor{gray!6}{13} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{home} & \cellcolor{gray!6}{1715} & \cellcolor{gray!6}{199}\\
resources & 30 & 13 & consortium & 24 & 9 & families & 13 & 5 & social & 1713 & 191\\
\cellcolor{gray!6}{healthy} & \cellcolor{gray!6}{29} & \cellcolor{gray!6}{16} & \cellcolor{gray!6}{region} & \cellcolor{gray!6}{23} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{way} & \cellcolor{gray!6}{12} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{different} & \cellcolor{gray!6}{1713} & \cellcolor{gray!6}{215}\\
routes & 27 & 13 & service & 22 & 11 & student & 12 & 5 & mobility & 1659 & 138\\
\cellcolor{gray!6}{lanes} & \cellcolor{gray!6}{26} & \cellcolor{gray!6}{3} & \cellcolor{gray!6}{•} & \cellcolor{gray!6}{21} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{region} & \cellcolor{gray!6}{12} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{significant} & \cellcolor{gray!6}{1650} & \cellcolor{gray!6}{208}\\

@@

\hypertarget{bigrams-and-concordances}{%
\subsection{4.2. Bigrams and
concordances}\label{bigrams-and-concordances}}

Bigrams for each policy corpora that occur more than 5 times are shown
in Figures \ref{fig:city-visual}, \ref{fig:consortia-visual}, and
\ref{fig:school-visual}. These figures help to make further sense of the
word frequencies reported above, and highlight the main ideas that are
presented to the public in each of the policy corpora. Municipalities
primarily discuss \emph{physical activity} (n = 53) and \emph{public
health} (n = 19) in the context of active travel. In addition,
\emph{travel planning} (n = 19), \emph{bike lanes} (n = 16), and
\emph{safe routes} (n = 14) are also identified, conceivably as
interventions and built environment factors that support AST. Key issues
related to transport such as \emph{traffic safety} (n = 10), \emph{air
quality} (n = 9), and \emph{greenhouse gases} (n = 9) are conveyed to
the public through AST documents. It is not surprising to find this
focus in AST documents given that municipalities in Ontario are
concerned about climate change and have increasingly looked to active
modes of travel to offset transport-related emissions in urban areas.
